\documentclass[11pt,a4paper,sans]{moderncv}

% ======= STYLE =======
\moderncvstyle{classic}
\moderncvcolor{blue}

% ======= PAGE LAYOUT =======
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3.2cm}

% ======= PERSONAL DATA =======
\name{Dr. Etienne}{Loire}
\title{Life Science Educator \& Researcher}
\address{50/310 Nghi Tam}{Hanoi, Vietnam}
\phone[mobile]{+33~(0)672286479}
\email{etienne.loire@gmail.com}
\social[researchgate]{https://www.researchgate.net/profile/Etienne-Loire}
\social[google]{https://scholar.google.com/citations?user=rxk_H-oAAAAJ}
\extrainfo{Born in 08/09/1980}
%\photo[64pt][0.4pt]{photo} % optional photo

% ======= DOCUMENT =======
\begin{document}

\makecvtitle

% ======= TEACHING PROFILE =======
\section{Profile}
\cvitem{}{
Experienced scientist with a solid foundation in biology, from molecular to ecosystems, specialized in genetics and bioinformatics, complemented by a strong international experience in science communication.  
Currently transitioning from a successful career in academic research to a dedicated focus on secondary education.  
Fluent in English and French, with significant teaching and mentoring experience in diverse cultural contexts across Southeast Asia.
}

% ======= TEACHING EXPERIENCE =======
\section{Teaching Experience}

\cventry{2006--2009}{Teaching Assistant}{University of Paris – Sorbonne}{Paris, France}{}{
\begin{itemize}
  \item Delivered 96 hours/year of tutorials and practicals in mathematics and computer science for biology undergraduates.
\end{itemize}
}

\cventry{2013--2019}{School Outreach Presenter}{Various High Schools and Middle Schools}{France}{}{
\begin{itemize}
  \item Conducted 1–2 day sessions each year to introduce students to scientific careers and research topics in an age-appropriate and engaging way.
\end{itemize}
}

\cventry{2015--2022}{Trainer, Genetic Data Analysis}{International Partners}{France}{}{
\begin{itemize}
  \item Developed curriculums and delivered tailored training sessions for students and adult learners on genetic and data analysis.
\end{itemize}
}

\cventry{2019--2022}{Guest Lecturer, Epidemiology}{Kasetsart University}{Bangkok, Thailand}{}{
\begin{itemize}
  \item Designed and delivered an English-language statistics in epidemiology course for international students from Thailand, Vietnam, Cambodia, Laos, and Indonesia.
\end{itemize}
}

\cventry{2025}{Private Tutor, AP Biology}{British International School of Hanoi}{Hanoi, Vietnam}{}{
\begin{itemize}
  \item Provided one-on-one tutoring in English for a final-year student preparing for AP Biology examinations.
\end{itemize}
}


% ======= EDUCATION =======
\section{Education}
\cventry{2006--2010}{Ph.D. in Evolutionary Genetics}{University of Paris – Sorbonne}{France}{}{}
\cventry{2004--2006}{Master’s in Cellular and Molecular Biology, specialization in Bioinformatics}{University of Paris – Sorbonne}{France}{ranked 2}{}
\cventry{2001--2004}{B.Sc. in Life Sciences}{University of Paris – Sorbonne}{France}{}{}

% ======= RESEARCH EXPERIENCE (SUMMARY) =======
\section{Research Experience}
\cventry{2015--2025}{Research Scientist}{CIRAD – French Agricultural Research Centre for International Development}{Vietnam/France}{}{
Led projects on microbial genomics, evolutionary biology, and antimicrobial resistance under the One Health framework.  
Managed partnerships with over 20 institutions in Southeast Asia. 
}

\cventry{2009--2015}{Postdoctoral Researcher}{CNRS, Max Planck Institute}{France/International}{}{
Conducted postdoctoral research in genomics, conservations, bioinformatics, and evolutionary biology 
}
\cvitem{}{Authors of 60 publications or conference acts, cited more than 2500 times in the scientific litterature}

% ======= TEACHING PHILOSOPHY =======
\section{Teaching Philosophy}
\cvitem{}{
My approach to teaching science is to foster curiosity and critical thinking while ensuring that students grasp the "big picture" and core concepts with clarity. 
I believe in building bridges between disciplines — for example, linking biology with mathematics, computer science, or environmental studies — and in creating a dynamic learning environment.
}

% ======= LANGUAGES =======
\section{Languages}
\cvitem{French}{Native (level C2)}
\cvitem{English}{Fluent (level C1/C2)}

% ======= IT SKILLS =======
\section{Skills}
\cvitem{Teaching}{Curriculum development, student mentoring, science communication}
\cvitem{Laboratory}{Microbiology, molecular and cellular biology, genetics, sequencing technologies}
\cvitem{Digital}{R, Python, dynamic dashboards, high-performance computing, web applications}
\cvitem{Soft skills}{Project management, international collaboration, conflict resolution, inclusive communication}

\end{document}

